Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity

### 2022-10-01 manuscript.Rmd
html

---
title: 'Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity
  Score Matching '
author: "Maria Eriksson"
output:
  word_document: default
  html_document: default
  pdf_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

Fourth step is to apply this model on patients from the Test Data. Using the model, the standard variable propensity score is calculated for each patient in the Test Data set. The propensity score determines the likelihood that a patient will receive ICU care, given their condition. If the model is suitable, it will correctly identify patients that did go to the ICU by awarding them high propensity scores, but non-ICU patients that were similar to this cohort will also get high propensity scores.

<!-- 
fråga: vi är ju ute efter ge vissa non-ICU pat höga propensity scores för att sedan kunna identifiera och filtrera fram dem i propensity score matchingen steg 5. Men hur identifierar man skillnaden mellan en patient som förmodligen borde fått ICU, och en patient modellen felaktigt spottat ut?
Och om man switchar över redan i steg 4 finns det ingen validering sen mera för dålig PSM i steg 5? -->

Fifth step is PSM. In PSM members of the subset that did not get ICU care are matched to patients who did go to the ICU, matching based on their propensity scores. There are a few different ways to perform this matching but they are all imperfect because propensity scores are unique and perfect matching is unattainable. There are control mechanisms and limitations but a risk of applying too fix or too loose matching criteria and inadvertently vastly under- or overestimate the  need of ICU beds remain.  
<!-- (b) Fråga: 1. visst finns dessa svagheter i propensity score matching?
2. vad gör man åt dem? 
3. är beskrivningen av åtgärder mot detta något som hör hemma här eller i results?-->

<!-- (b) Describe any methods used to examine subgroups and interactions -->

>>>>

---
title: 'Quantifying unmet ICU beds in tertiary hospitals in urban India using Propensity
  Score Matching '
author: "Maria Eriksson"
output:
  html_document: default
  word_document: default
  pdf_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

Fourth step is to apply this model on patients from the Test Data. Using the model, the standard variable propensity score is calculated for each patient in the Test Data set. The propensity score determines the likelihood that a patient will receive ICU care, given their condition. If the model is suitable, it will correctly identify patients that did go to the ICU by awarding them high propensity scores, but non-ICU patients that were similar to this cohort will also get high propensity scores. 
<!-- 
fråga: vi är ju ute efter ge vissa non-ICU pat höga propensity scores för att sedan kunna identifiera och filtrera fram dem i propensity score matchingen steg 5. Men hur identifierar man skillnaden mellan en patient som förmodligen borde fått ICU, och en patient modellen felaktigt spottat ut?
Och om man switchar över redan i steg 4 finns det ingen validering sen mera för dålig PSM i steg 5? -->

Fifth step is PSM. In PSM members of the subset that did not get ICU care are matched to patients who did go to the ICU, matching based on their propensity scores. There are a few different ways to perform this matching but they are all imperfect because propensity scores are unique and perfect matching is unattainable. There are control mechanisms and limitations but a risk of applying too fix or too loose matching criteria and inadvertently vastly under- or overestimate the  need of ICU beds remain.  
<!-- (b) Fråga: 1. visst finns dessa svagheter i propensity score matching?
2. vad gör man åt dem? 
3. är beskrivningen av åtgärder mot detta något som hör hemma här eller i results?-->
<!-- (b) Describe any methods used to examine subgroups and interactions -->
